ShrinkNets: Learning Network Size while Training

### 2018-02-09 paper/ICML/paper.tex
changed speedup number
updated abstract

\begin{abstract}
As neural networks are being widely in different applications and
on different hardware, it has become increasingly important to optimize
inference time and model size along with model accuracy.  Most current work
optimizes model size, model accuracy and inference time in different stages, 
resulting in suboptimal results and computational inefficiency.  In
this work, we propose a new technique called ShrinkNets that optimizes all three
of these metrics simultaneously by learning optimal network size at training
time.  Specifically our technique presents a new method to simultaneously
optimize network size and model performance by neuron-level pruning.
Neuron-level pruning not only produces much smaller networks for a given
accuracy threshold but also produces dense weight matrices that are efficient at
inference time.  By applying our technique to a variety of models with both
convolutional and fully connected layers, we show that ShrinkNets can reduce network size
by 35x in comparison to to a static network on \texttt{CIFAR10}, with
6x improvement in inference time. In addition, the
most accurate networks found by ShrinkNets are similar or more accurate than
those found by statically trained networks.  
\end{abstract}

@@

\clearpage

>>>>

\begin{abstract}
As neural networks become widely deployed in different applications and 
on different
hardware, it has become increasingly important to optimize inference time and
model size along with model accuracy.  
Most current techniques optimize model size,
model accuracy and inference time in different stages, resulting in suboptimal
results and computational inefficiency.  
In this work, we propose a new
technique called \shrink that optimizes all three of these metrics
simultaneously.  
Specifically we present a new method to simultaneously optimize network size and
model performance by neuron-level pruning during training.  
Neuron-level pruning not only
produces much smaller networks for a given accuracy threshold but also produces
dense weight matrices that are amenable to efficient inference.  
By applying our
technique to convolutional as well as fully connected models, we show that 
\shrink can reduce network size by 35X with a 6X improvement in inference time.
In addition, the most accurate networks found by \shrink have accuracy that is
similar to or better than those found by statically-sized networks.  
\end{abstract}

@@
